---
title: "R Notebook"
output: html_notebook
---

```{r}
library(bslib)
library(dplyr)
library(ggplot2)
library(ggExtra)
library(DT)
library(plotly)
library(scales)
library(qs)
```


```{r}
# linked_data <- read.delim(gzfile("C:/Users/sthompson5/Documents/Meat Consumption/data/animal_products.csv.gz")) %>%  as_tibble() %>% select(-BEGIN_CODE:-END_CODE, -WEEK_ENDING:-LOAD_TIME )
# 
# state_lookup <- tibble(
#     STATE_NAME = toupper(state.name),
#     STATE_ABB = toupper(state.abb)
# )

```

```{r}
# pre_filtered <- linked_data %>% 
#     filter(SOURCE_DESC == "SURVEY",
#            UNIT_DESC == "HEAD",
#            AGG_LEVEL_DESC == "STATE",
#            DOMAIN_DESC == "TOTAL",
#            LOCATION_DESC != "NEW ENGLAND"
#            ) %>%
#     mutate(STATISTICCAT_DESC = ifelse(grepl("CONDEMNED", STATISTICCAT_DESC, ignore.case = TRUE), "CONDEMNED", STATISTICCAT_DESC)) %>% 
#     select(-STATE_ANSI:-COUNTRY_NAME, -CV_., STATE_NAME, -SOURCE_DESC, -AGG_LEVEL_DESC) %>% 
#     mutate(VALUE = as.numeric(gsub(",", "", VALUE))) %>% 
#     filter(!is.na(VALUE)) %>% 
#     arrange(YEAR) %>% 
#     left_join(state_lookup, by = "STATE_NAME")
# print(object.size(pre_filtered), units = "auto")
# 
# 
# qsave(pre_filtered, "Filtered_USDA_Data.qs")
```



```{r}
pre_filtered <- qread("C:/Users/sthompson5/Documents/Meat Consumption/Filtered_USDA_Data.qs")


all_chicken <- pre_filtered %>% 
    filter(FREQ_DESC == "ANNUAL",
           COMMODITY_DESC == "CHICKENS"
           ) %>% 
    group_by(YEAR, STATE_ABB, STATE_NAME, STATISTICCAT_DESC, UNIT_DESC) %>% 
    summarise(VALUE = sum(VALUE)) %>% 
    mutate(FREQ_DESC = "ANNUAL")

```

```{r}
all_cattle <- pre_filtered %>% 
    filter(FREQ_DESC == "ANNUAL",
           COMMODITY_DESC == "CATTLE",
           CLASS_DESC %in% c("HEIFERS", "CALVES", "BULLS","STEERS", "COWS")) %>% 
    group_by(YEAR, STATE_ABB, STATE_NAME, STATISTICCAT_DESC, UNIT_DESC, CLASS_DESC, SHORT_DESC) %>% 
    summarise(VALUE = sum(VALUE))
all_cattle %>% sapply(unique)

```

```{r}
test1 <- pre_filtered %>% 
    filter(STATE_NAME %in% sort(unique(STATE_NAME))[10:20]) %>% 
    filter(FREQ_DESC == "ANNUAL",
           COMMODITY_DESC == "CATTLE",
           CLASS_DESC == "CALVES",
           SHORT_DESC == "CATTLE, CALVES, SLAUGHTER, COMMERCIAL - SLAUGHTERED, MEASURED IN HEAD"
           ) %>% 
    group_by(YEAR, STATE_NAME, STATISTICCAT_DESC, UNIT_DESC, CLASS_DESC, SHORT_DESC) %>% 
    summarise(VALUE = sum(VALUE)) %>% 
    arrange(STATE_NAME) 

test2 <- pre_filtered %>% 
    filter(STATE_NAME %in% sort(unique(STATE_NAME))[10:20]) %>% 
    filter(FREQ_DESC == "ANNUAL",
           COMMODITY_DESC == "CATTLE",
           CLASS_DESC == "CALVES",
           SHORT_DESC ==  "CATTLE, CALVES, SLAUGHTER, COMMERCIAL, FI - SLAUGHTERED, MEASURED IN HEAD"
           ) %>% 
    group_by(YEAR, STATE_NAME, STATISTICCAT_DESC, UNIT_DESC, CLASS_DESC, SHORT_DESC) %>% 
    summarise(VALUE = sum(VALUE)) %>% 
    arrange(STATE_NAME)


ggplot()+
    geom_point(data = test1, 
               aes(x = YEAR,
                   y = VALUE),
               color = "red") +
    geom_point(data = test2,
               aes(x = YEAR,
                   y = VALUE),
               color = "blue")+
    facet_wrap(~ STATE_NAME)
